Ecosystem size and complexity as extrinsic drivers of food chain length in branching ecosystems

### 2023-03-27 rmd/manuscript.Rmd
edit

where $e_{ij}$ is the energetic conversion efficiency from $i$ to $j$. The function $g(\cdot)$ defines the density-dependent recruitment for the basal species, and the function $f_k(\cdot)$ dictates the proportion of survived prey individuals after predation. In the above equations, we re-defined variables as follows to simplify the expression:

@@

We also calculated the proportion of the patch state ("No species", "B", "B + C", "B + P", and "B + C + P") at each time step to infer mechanisms that drive changes in FCL. The time-averaged proportion of patch state $\bar{s}$ was obtained as $\bar{s} = \frac{s_t}{N_p T}$, where $s_t$ is the number of patches in a given patch state at time step $t$.

@@

We obtained the global FCL $\bar{\tau}$ and $\bar{s}$ for the last `r unique(df_sim$n_timestep)` time steps. All analysis was performed in R 4.2.1 [@rcoreteamLanguageEnvironmentStatistical2021]

>>>>

where $e_{ij}$ is the energetic conversion efficiency from $i$ to $j$. The function $g(\cdot)$ defines the density-dependent recruitment for the basal species, and the function $f_k(\cdot)$ dictates the proportion of survived prey individuals after predation (see equation (8) below). In the above equations, we re-defined variables as follows to simplify the expression:

@@

We also calculated the proportion of the patch state ("No species", "B", "B + C", "B + P", and "B + C + P") at each time step to infer mechanisms that drive changes in FCL. The time-averaged proportion of patch state $\bar{\psi}$ was obtained as $\bar{\psi} = \frac{q_t}{N_p T}$, where $q_t$ is the number of patches in a given patch state at time step $t$.

@@

We obtained the global FCL $\bar{\tau}$ and the proportion of the patch state $\bar{\psi}$ for the last `r unique(df_sim$n_timestep)` time steps. All analysis was performed in R 4.2.1 [@rcoreteamLanguageEnvironmentStatistical2021]
